Methodology for Assessing the State of the Practice for Domain X

### 2020-12-11 StateOfPractice/Methodology/Methodology.tex
fixed error in Section 11 Methodology

An AHP pairwise comparison between the short list packages with respect to
usability and modifiability survey results is conducted by the domain
expert. The tool can be found here. The usability and modifiability survey can
be found
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Experiments.pdf}
{here}. This step is intended to start a conversation about the relative quality of
short-listed software packages.

>>>>

An AHP pairwise comparison between the short list packages with respect to
usability and modifiability survey results is conducted, and then reviewed by the domain expert. The tool can be found here. The usability and modifiability survey can be found
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Experiments.pdf}
{here}. This step is intended to start a conversation about the relative quality of short-listed software packages.
